\pkg{Rgbp}: An \proglang{R} Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data

### 2015-07-02 jss/article_v2.tex
draft and code

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Hyungsuk Tak, Joseph Kelly, Carl Morris} %% comma-separated
\Plaintitle{Rgbp: Hierarchical Modeling and Frequency Method Checking} %% without formatting
\Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% a short title (if necessary)
%% an abstract and keywords
\Abstract{
\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data. The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as averages or proportions, possibly together with covariates of each group but without population-level data. The approximate Bayesian tool equipped with the adjustment for density maximization produces point and interval estimates for each random effect, point estimates and their standard errors for regression coefficients, and a point estimate and its standard error for a second-level variance component. For the Binomial data, the package provides an option to draw independent  posterior samples of all the model parameters from their  posterior distributions via the acceptance-rejection method.  The main goal of \pkg{Rgb} is to produce approximate, or exact for the Binomial model, Bayesian interval estimates for the random effects that meet their nominal confidence levels.   For this purpose, our models adopt unique improper hyper-prior distributions and \pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
% and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects
%It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
\Keywords{overdispersion, hierarchical model, adjustment for density maximization, acceptance-rejection method, repeated sampling coverage evaluation, frequency method checking, \proglang{R}}
\Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 
%% without formatting
%% at least one keyword must be supplied

@@

\subsection[Hyper-prior distributions]{Hyper-prior Distribution}
Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. With the goal of objectivity in mind, our choice for the hyper-prior distributions is
\begin{equation}\label{eq:hyper}
\boldsymbol{\beta} \sim \textrm{Uniform on}~ \textbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
\end{equation}

@@

The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail. For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out, see  \cite{tang2011}.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=6cm]{process.png}
\caption{Pseudo-data generating process}
\label{fig:pseudo}
\end{center}
\end{figure}

@@

These data can be loaded into \proglang{R} using the following code.
\begin{CodeChunk}
\begin{CodeInput}
R> library(Rgbp)
R> data(hospital)
R> y <- hospital$d
R> n <- hospital$n
\end{CodeInput}
\end{CodeChunk}

@@

         obs.mean    n prior.mean shrinkage low.intv post.mean upp.intv post.sd
1          0.0448   67       0.03     0.911   0.0199    0.0313   0.0454 0.00653
2          0.0294   68       0.03     0.910   0.0189    0.0299   0.0435 0.00631
3          0.0238  210       0.03     0.765   0.0185    0.0285   0.0407 0.00566
4          0.0430  256       0.03     0.728   0.0225    0.0335   0.0467 0.00619
5          0.0335  269       0.03     0.718   0.0208    0.0310   0.0432 0.00573
6          0.0438  274       0.03     0.714   0.0229    0.0339   0.0472 0.00621
7          0.0432  278       0.03     0.711   0.0228    0.0338   0.0469 0.00617
8          0.0136  295       0.03     0.699   0.0157    0.0250   0.0366 0.00534
9          0.0288  347       0.03     0.663   0.0200    0.0296   0.0410 0.00536
10         0.0372  349       0.03     0.662   0.0222    0.0325   0.0446 0.00571
11         0.0391  358       0.03     0.656   0.0228    0.0331   0.0454 0.00579
12         0.0177  396       0.03     0.633   0.0165    0.0255   0.0363 0.00506
13         0.0278  431       0.03     0.613   0.0200    0.0292   0.0400 0.00511
14         0.0249  441       0.03     0.608   0.0191    0.0280   0.0387 0.00502
15         0.0273  477       0.03     0.589   0.0199    0.0289   0.0394 0.00499
16         0.0455  484       0.03     0.585   0.0256    0.0364   0.0491 0.00601
17         0.0304  494       0.03     0.580   0.0211    0.0302   0.0409 0.00506
18         0.0220  501       0.03     0.577   0.0180    0.0266   0.0369 0.00483
19         0.0277  505       0.03     0.575   0.0202    0.0290   0.0395 0.00494
20         0.0204  540       0.03     0.559   0.0173    0.0258   0.0358 0.00474
21         0.0284  563       0.03     0.548   0.0206    0.0293   0.0395 0.00485
22         0.0236  593       0.03     0.535   0.0187    0.0270   0.0369 0.00466
23         0.0150  602       0.03     0.532   0.0147    0.0230   0.0329 0.00466
24         0.0238  629       0.03     0.521   0.0188    0.0271   0.0368 0.00460
25         0.0204  636       0.03     0.518   0.0173    0.0254   0.0351 0.00455
26         0.0480  729       0.03     0.484   0.0286    0.0393   0.0516 0.00587
27         0.0306  849       0.03     0.446   0.0223    0.0303   0.0397 0.00445
28         0.0274  914       0.03     0.428   0.0208    0.0285   0.0374 0.00423
29         0.0213  940       0.03     0.421   0.0176    0.0249   0.0335 0.00407
30         0.0293 1193       0.03     0.364   0.0223    0.0296   0.0379 0.00397
31         0.0201 1340       0.03     0.338   0.0170    0.0235   0.0310 0.00360
colMeans           517       0.03     0.600   0.0201    0.0293   0.0403 0.00517
\end{CodeOutput}
\end{CodeChunk}

@@

Second-level Variance Component Estimation Summary:
alpha = log(A) for Gaussian or alpha = log(1/r) for Binomial and Poisson data:

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(p.output)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 2.5in]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
\label{fig:hospshr}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> p.coverage <- coverage(p.output, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 2.5in]{hospital2.png}
\caption{Coverage plot via frequency method checking for 31 hospitals}
\label{fig:hospitalcoverage}
\end{center}
\end{figure}

@@

The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (groups) to test whether students (units) SAT scores are effected by coaching. The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}. We can load this data set into \proglang{R} by the following codes.
\begin{CodeChunk}
\begin{CodeInput}
R> library(Rgbp)
R> data(schools)
R> y  <- schools$y
R> se <- schools$se
\end{CodeInput}
\end{CodeChunk}

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
This output from \code{gbp} summarizes the results. In this Gaussian hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$. As such, schools whose variation within the school ($V_{j}$) is less than the between school variation ($A$) will shrink greater than $50\%$. The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit due to the fact that every school's $95\%$ posterior interval contains 0. In the case where the number of groups is large \pkg{Rgbp} provides a summary feature:

@@

\begin{figure}[h] 
\begin{center}
\includegraphics[width = 2.5in]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools}
\label{fig:8schoolsplot}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> g.coverage <- coverage(g.output, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 2.5in]{school2.png}
\caption{Coverage plot via frequency method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}

@@

The data of 18 major league baseball players contain the batting averages through their first 45 official at-bats of the 1970 season \citep{1975}. We add a covariate about their outfielder indicators taking on 1 if a player is an outfielder and 0 otherwise. We can load the data into \proglang{R} with the following codes.
\begin{CodeChunk}
\begin{CodeInput}
R> library(Rgbp)
R> data(baseball)
R> y <- baseball$Hits
R> n <- baseball$At.Bats
R> x <- ifelse(baseball$Position == "fielder", 1, 0)
\end{CodeInput}
\end{CodeChunk}
%$
Conditioning on the unknown true batting average (random effect) for each player we assume that the at-bats are independent and therefore, $y_{j}\vert p_{j}\stackrel{indep.}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$. Our goal is to obtain point and interval estimates of each random effect, $p_j$, whilst considering the additional information on whether the player is an outfielder or not. The function \code{gbp} provides a way to incorporate such covariate information seamlessly into the conjugate Beta prior distribution so that the regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately. %For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.

@@

         obs.mean  n   X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429  0.0462
2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420  0.0448
3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411  0.0437
4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403  0.0429
5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396  0.0424
6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341  0.0415
7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331  0.0400
8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323  0.0388
9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315  0.0380
10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379  0.0432
11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302  0.0377
17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297  0.0381
18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292  0.0389
colMeans          45 0.44      0.267     0.715    0.191     0.267    0.351  0.0410
\end{CodeOutput}
\end{CodeChunk}
% Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also

@@

The regression coefficient for the outfielder indicator is significant, considering that p-value for $\hat{\beta}_2$ is 0.038. It means that the  two estimates for the expected random effects for the outfielders and infielders are significantly different. Also, the positive sign of $\hat{\beta}_{2}$ indicates that the population batting average for all outfielders tends to be higher than that for infielders. The  estimated odds ratio is $\exp(0.389)=1.48$.

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b.output)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h!]
\begin{center}
\includegraphics[width = 2.5in]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
\label{fig:baseball}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> b.coverage <- coverage(b.output, nsim = 1000) 
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h!]
\begin{center}
\includegraphics[width = 2.5in]{baseball2.png}
\caption{Coverage plot via frequency method checking for 18 players}
\label{fig:baseball2}
\end{center}
\end{figure}

@@

\section[acknowledgments]{Acknowledgments}
The authors thank Professor Cindy Christiansen, Professor Phil Everson and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.

@@

>>>>

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Hyungsuk Tak, Joseph Kelly, Carl Morris} %% comma-separated
\Plaintitle{Rgbp: An R Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% without formatting
\Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% a short title (if necessary)
%% an abstract and keywords
\Abstract{
\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data. The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as averages or proportions, possibly together with covariates of each group but without population-level data. The approximate Bayesian tool equipped with the adjustment for density maximization produces point and interval estimates for each random effect, point estimates and their standard errors for regression coefficients, and a point estimate and its standard error for a second-level variance component. For the Binomial data, the package provides an option to draw independent  posterior samples of all the model parameters from their  posterior distributions via the acceptance-rejection method.  The main goal of \pkg{Rgb} is to produce approximate, or exact for the Binomial model, Bayesian interval estimates for the random effects that meet their nominal confidence levels.   For this purpose, our models adopt unique improper hyper-prior distributions and \pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
% and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects
%It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
\Keywords{overdispersion, hierarchical model, adjustment for density maximization, acceptance-rejection method, repeated sampling coverage evaluation, frequency method checking, \proglang{R}}
\Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 
%% without formatting
%% at least one keyword must be supplied

@@

\subsection[Hyper-prior distributions]{Hyper-prior distribution}
Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. With the goal of objectivity in mind, our choice for the hyper-prior distributions is
\begin{equation}\label{eq:hyper}
\boldsymbol{\beta} \sim \textrm{Uniform on}~ \textbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
\end{equation}

@@

The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \citep[see]{berger1999integrated} for the integrated likelihood in detail. For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out, see  \cite{tang2011}.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=6cm]{process.png}
\caption{Pseudo-data generating process.}
\label{fig:pseudo}
\end{center}
\end{figure}

@@

These data can be loaded into \proglang{R} using the following code.
\begin{CodeChunk}
\begin{CodeInput}
R> library(``Rgbp'')
R> data(``hospital'')
R> y <- hospital$d
R> n <- hospital$n
\end{CodeInput}
\end{CodeChunk}

@@

      obs.mean    n prior.mean shrinkage low.intv post.mean upp.intv post.sd
1       0.0448   67       0.03     0.911   0.0199    0.0313   0.0454 0.00653
2       0.0294   68       0.03     0.910   0.0189    0.0299   0.0435 0.00631
3       0.0238  210       0.03     0.765   0.0185    0.0285   0.0407 0.00566
4       0.0430  256       0.03     0.728   0.0225    0.0335   0.0467 0.00619
5       0.0335  269       0.03     0.718   0.0208    0.0310   0.0432 0.00573
6       0.0438  274       0.03     0.714   0.0229    0.0339   0.0472 0.00621
7       0.0432  278       0.03     0.711   0.0228    0.0338   0.0469 0.00617
8       0.0136  295       0.03     0.699   0.0157    0.0250   0.0366 0.00534
9       0.0288  347       0.03     0.663   0.0200    0.0296   0.0410 0.00536
10      0.0372  349       0.03     0.662   0.0222    0.0325   0.0446 0.00571
11      0.0391  358       0.03     0.656   0.0228    0.0331   0.0454 0.00579
12      0.0177  396       0.03     0.633   0.0165    0.0255   0.0363 0.00506
13      0.0278  431       0.03     0.613   0.0200    0.0292   0.0400 0.00511
14      0.0249  441       0.03     0.608   0.0191    0.0280   0.0387 0.00502
15      0.0273  477       0.03     0.589   0.0199    0.0289   0.0394 0.00499
16      0.0455  484       0.03     0.585   0.0256    0.0364   0.0491 0.00601
17      0.0304  494       0.03     0.580   0.0211    0.0302   0.0409 0.00506
18      0.0220  501       0.03     0.577   0.0180    0.0266   0.0369 0.00483
19      0.0277  505       0.03     0.575   0.0202    0.0290   0.0395 0.00494
20      0.0204  540       0.03     0.559   0.0173    0.0258   0.0358 0.00474
21      0.0284  563       0.03     0.548   0.0206    0.0293   0.0395 0.00485
22      0.0236  593       0.03     0.535   0.0187    0.0270   0.0369 0.00466
23      0.0150  602       0.03     0.532   0.0147    0.0230   0.0329 0.00466
24      0.0238  629       0.03     0.521   0.0188    0.0271   0.0368 0.00460
25      0.0204  636       0.03     0.518   0.0173    0.0254   0.0351 0.00455
26      0.0480  729       0.03     0.484   0.0286    0.0393   0.0516 0.00587
27      0.0306  849       0.03     0.446   0.0223    0.0303   0.0397 0.00445
28      0.0274  914       0.03     0.428   0.0208    0.0285   0.0374 0.00423
29      0.0213  940       0.03     0.421   0.0176    0.0249   0.0335 0.00407
30      0.0293 1193       0.03     0.364   0.0223    0.0296   0.0379 0.00397
31      0.0201 1340       0.03     0.338   0.0170    0.0235   0.0310 0.00360
Mean            517       0.03     0.600   0.0201    0.0293   0.0403 0.00517
\end{CodeOutput}
\end{CodeChunk}

@@

Second-level Variance Component Estimation Summary:
alpha=log(A) for Gaussian or alpha=log(1/r) for Binomial and Poisson data:

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(p.output)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 2.8in]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot for 31 hospitals.}
\label{fig:hospshr}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> p.coverage <- coverage(p.output, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 2.8in]{hospital2.png}
\caption{Coverage plot via frequency method checking for 31 hospitals.}
\label{fig:hospitalcoverage}
\end{center}
\end{figure}

@@

The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (groups) to test whether students (units) SAT scores are effected by coaching. The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}. We can load this data set into \proglang{R} by the following codes.
\begin{CodeChunk}
\begin{CodeInput}
R> library(``Rgbp'')
R> data(``schools'')
R> y  <- schools$y
R> se <- schools$se
\end{CodeInput}
\end{CodeChunk}

@@

     obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5       -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2        8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7       18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4        7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6        1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1       28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3       -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8       12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
Mean          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
This output from \code{gbp} summarizes the results. In this Gaussian hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$. As such, schools whose variation within the school ($V_{j}$) is less than the between school variation ($A$) will shrink greater than $50\%$. The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit due to the fact that every school's $95\%$ posterior interval contains 0. In the case where the number of groups is large \pkg{Rgbp} provides a summary feature:

@@

\begin{figure}[h] 
\begin{center}
\includegraphics[width = 2.8in]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools.}
\label{fig:8schoolsplot}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> g.coverage <- coverage(g.output, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 2.8in]{school2.png}
\caption{Coverage plot via frequency method checking for 8 schools.}
\label{fig:schoolcoverage}
\end{center}
\end{figure}

@@

The data of 18 major league baseball players contain the batting averages through their first 45 official at-bats of the 1970 season \citep{1975}. We add a covariate about their outfielder indicators taking on 1 if a player is an outfielder and 0 otherwise. We can load the data into \proglang{R} with the following codes.
\begin{CodeChunk}
\begin{CodeInput}
R> library(``Rgbp'')
R> data(``baseball'')
R> y <- baseball$Hits
R> n <- baseball$At.Bats
R> x <- ifelse(baseball$Position == "fielder", 1, 0)
\end{CodeInput}
\end{CodeChunk}
%$
Conditioning on the unknown true batting average (random effect) for each player we assume that the at-bats are independent and therefore, $y_{j}\vert p_{j}\stackrel{indep.}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$. Our goal is to obtain point and interval estimates of each random effect, $p_j$, whilst considering the additional information on whether the player is an outfielder or not. The function \code{gbp} provides a way to incorporate such covariate information seamlessly into the conjugate Beta prior distribution so that the regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately. %For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.

@@

     obs.mean  n  X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
1       0.400 45 1.0      0.310     0.715    0.248     0.335    0.429  0.0462
2       0.378 45 1.0      0.310     0.715    0.244     0.329    0.420  0.0448
3       0.356 45 1.0      0.310     0.715    0.240     0.323    0.411  0.0437
4       0.333 45 1.0      0.310     0.715    0.236     0.316    0.403  0.0429
5       0.311 45 1.0      0.310     0.715    0.230     0.310    0.396  0.0424
6       0.311 45 0.0      0.233     0.715    0.179     0.256    0.341  0.0415
7       0.289 45 0.0      0.233     0.715    0.175     0.249    0.331  0.0400
8       0.267 45 0.0      0.233     0.715    0.171     0.243    0.323  0.0388
9       0.244 45 0.0      0.233     0.715    0.166     0.237    0.315  0.0380
10      0.244 45 1.0      0.310     0.715    0.210     0.291    0.379  0.0432
11      0.222 45 0.0      0.233     0.715    0.161     0.230    0.308  0.0377
12      0.222 45 0.0      0.233     0.715    0.161     0.230    0.308  0.0377
13      0.222 45 0.0      0.233     0.715    0.161     0.230    0.308  0.0377
14      0.222 45 1.0      0.310     0.715    0.202     0.285    0.375  0.0441
15      0.222 45 1.0      0.310     0.715    0.202     0.285    0.375  0.0441
16      0.200 45 0.0      0.233     0.715    0.155     0.224    0.302  0.0377
17      0.178 45 0.0      0.233     0.715    0.148     0.218    0.297  0.0381
18      0.156 45 0.0      0.233     0.715    0.140     0.211    0.292  0.0389
Mean          45 0.4      0.267     0.715    0.191     0.267    0.351  0.0410
\end{CodeOutput}
\end{CodeChunk}
% Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also

@@

The regression coefficient for the outfielder indicator is significant, considering that $p$~value for $\hat{\beta}_2$ is 0.038. It means that the  two estimates for the expected random effects for the outfielders and infielders are significantly different. Also, the positive sign of $\hat{\beta}_{2}$ indicates that the population batting average for all outfielders tends to be higher than that for infielders. The  estimated odds ratio is $\exp(0.389)=1.48$.

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b.output)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h!]
\begin{center}
\includegraphics[width = 2.8in]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot for 18 baseball players.}
\label{fig:baseball}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> b.coverage <- coverage(b.output, nsim = 1000) 
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h!]
\begin{center}
\includegraphics[width = 2.8in]{baseball2.png}
\caption{Coverage plot via frequency method checking for 18 players.}
\label{fig:baseball2}
\end{center}
\end{figure}

@@

@@

\section*{Acknowledgments}
The authors thank Professor Cindy Christiansen, Professor Phil Everson and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
